\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{booktabs}
\usepackage{amsmath}

\title{High-Capacity LSTM Analysis: 8 Futures and \$100 Simulation}
\author{Gemini CLI Agent}
\date{February 18, 2026}

\begin{document}

\maketitle

\section{Introduction}
This report evaluates a high-capacity LSTM model (512 neurons, 2 layers) trained on 8 futures symbols (ES, NQ, RTY, CL, GC, MES, MNQ, M2K). A trading simulation was performed on an unseen out-of-sample test set (last 20\% of the 60-day 10-min data) to assess the feasibility of starting with a \$100 account.

\section{Model and Data}
\begin{itemize}
    \item \textbf{Architecture:} 2-layer LSTM with 512 hidden units.
    \item \textbf{Input Features:} 8 futures (E-mini and Micro contracts).
    \item \textbf{Target:} Micro E-mini S\&P 500 (MES) next 10-min price.
    \item \textbf{Training duration:} 120 seconds.
\end{itemize}

\section{Simulation Parameters}
\begin{itemize}
    \item \textbf{Initial Capital:} \$100.00
    \item \textbf{Asset:} MES (Micro E-mini S\&P 500).
    \item \textbf{Contract Multiplier:} \$5.00 per point.
    \item \textbf{Commissions:} \$1.50 per round-trip trade.
    \item \textbf{Strategy:} Directional prediction (Long if $Pred_{t+1} > Price_t$, Short otherwise).
\end{itemize}

\section{Results}
\begin{center}
\begin{tabular}{lr}
\toprule
Metric & Value \\
\midrule
Initial Capital & \$100.00 \\
Final Capital (Out-of-Sample) & \$0.00 \\
Net Profit/Loss & -\$100.00 \\
\bottomrule
\end{tabular}
\end{center}

\section{Analysis}
The simulation resulted in a total loss of the initial \$100 capital. Several factors contribute to this outcome:
\begin{enumerate}
    \item \textbf{Undercapitalization:} A \$100 account provides no buffer for drawdowns. In futures trading, even Micro contracts (MES) move significantly. A 20-point move against the position results in a \$100 loss, which is 100\% of the account.
    \item \textbf{Transaction Costs:} At \$1.50 per 10-minute trade, commissions rapidly erode a small account. Over many trades, this fixed cost creates a significant hurdle for profitability.
    \item \textbf{Model Accuracy:} While a 512-neuron LSTM is a powerful architecture, directional prediction of high-frequency futures prices is notoriously difficult and susceptible to noise.
    \item \textbf{Margin Requirements:} In a real-world scenario, a broker would likely liquidate the position long before the account reaches zero due to maintenance margin requirements.
\end{enumerate}

\section{Conclusion}
Starting with \$100 to trade futures, even with a sophisticated 512-neuron LSTM model, is extremely high risk and statistically likely to result in total capital loss. A much larger capital base (at least \$2,000-\$5,000) is required to withstand the inherent volatility and transaction costs of the futures market.

\end{document}
